Clustering Analysis of Mobility Data

### 2018-07-10 dokumentation/data_findings.tex
Weiter an der analyse der Daten gearbeitet. Werde gerade gezwungen zum griechen zu gehen.... to be continued

\end{figure}
	\end{minipage}
\begin{minipage}{0.48\textwidth}
	We are looking for clusters inside the whole dataset by generating different charts which visualize a subset of attributes of all data points. Firstly, before neglecting the strata data of the data set, we consider chart \ref{fig:strata_reason_age} which visualizes the different reasons why people move at which age grouped by socio-economic classes. Throughout the classes each cloud of points is very similar, i. e. young people are mostly studying, adults are mostly working and older people are moving for recreation or health. Therefore categorizing people by taking the reason for their movements into account is not an option. The only difference that is not caused by outliers is the smaller size of the first and last economic class.

>>>>

\end{figure}
\begin{figure}[H]
	\centering

	\centering
	\includegraphics[width=3.0in]{../Martin-RapidMiner/diagramme/origin_destination_reason_lowJitter.png}
	\caption{Reason for movements from origin to destination}
	\label{fig:origin_destination_reason}

\end{figure}
	\end{minipage}
\begin{minipage}{0.48\textwidth}
	We are looking for clusters inside the whole dataset by generating different charts which visualize a subset of attributes of all data points. Firstly, before neglecting the strata data of the data set, we consider chart \ref{fig:strata_reason_age} which visualizes the different reasons why people move at which age grouped by socio-economic classes. Throughout the classes each cloud of points is very similar, i. e. young people are mostly studying, adults are mostly working and older people are moving for recreation or health. Therefore categorizing people by taking the reason for their movements into account is not an option. The only difference that is not caused by outliers is the smaller size of the first and last economic class.\\

	In figure \ref{fig:origin_destination_reason} we see the reason (color of dots) why people move from their origin to a destination. It can be seen, that the vast majority of people are working and that there are metropoliton areas inside the city.
